### 2015-04-16 docs/ms.Rmd
Fix author affiliations, add highlights & acknowledgements

Thomas E. White^2,7^, Rhiannon L. Dalrymple^1,7^, Daniel W. A. Noble^2,7^, James C. O’Hanlon ^2,7^, Daniel B. Zurek^5,7^, Kate D. L. Umbers^3,4,6,7^

^1^ Evolution & Ecology Research Centre, School of Biological, Earth and Environmental Sciences, University of New South Wales, Kensington, NSW, Australia, 2022 ^2^ Department of Biological Sciences, Macquarie University, North Ryde, NSW, Australia, 2109 ^3^ School of Biological Sciences, University of Wollongong, Wollongong, NSW, Austrlaia 2252 ^4^ Centre for Evolutionary Biology, University of Western Australia, Crawley, WA, Australia 6008 ^5^ Department of Biological Sciences, University of Pittsburgh, Pittsburgh, PA, USA, 15260 ^6^ School of Science and Health, University of Western Sydney Hawkesbury, NSW, Australia 2751

@@

Corresponding Author:

@@

Phone: +61 2 9850 6279

E-mail: thomas.white@mq.edu.au

Keywords: spectrometry, photography, visual ecology, pigment, structural colour, visual modelling, methods

@@

>>>>

Thomas E. White^1,7^, Rhiannon L. Dalrymple^2,7^, Daniel W. A. Noble^1,2,7^, James C. O’Hanlon ^1,7^, Daniel B. Zurek^3,7^, Kate D. L. Umbers^4,5,6,7^

^1^ Department of Biological Sciences, Macquarie University, North Ryde, NSW, Australia, 2109 ^2^ Evolution & Ecology Research Centre, School of Biological, Earth and Environmental Sciences, University of New South Wales, Kensington, NSW, Australia, 2022 ^3^ Department of Biological Sciences, University of Pittsburgh, Pittsburgh, PA, USA, 15260 ^4^ School of Biological Sciences, University of Wollongong, Wollongong, NSW, Austrlaia 2252 ^5^ Centre for Evolutionary Biology, University of Western Australia, Crawley, WA, Australia 6008 ^6^ School of Science and Health, University of Western Sydney Hawkesbury, NSW, Australia 2751

@@

**Corresponding Author:**

@@

**Phone:** +61 2 9850 6279

**E-mail:** thomas.white@mq.edu.au

**Keywords:** methods, photography, pigment, spectrometry, structural colour, visual ecology, visual modelling

**Highlights:**

- We review the reproducibility of contemporary studies of biological coloration.
- Methodological details are often missing, and data are seldom publicly available.
- We present guidelines for methods reporting, and for improving reproducibility.

@@

## Acknowledgements
We thank Rafael Maia, the Morehouse lab, and three anonymous reviewers for valuable discussions and suggestions. TEW and RLD were supported by Australian Postgraduate Awards, and DWAN was supported by an NSERC PGSD and MQRES scholarship.
